Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-20 qhtv2.tex
Clarifications

\subsection{Parameter Tuning}
The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.

@@

\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]

@@

\section{Experiments and Benchmarks}
In this section, we present the different experiments we made. The code is accessible online and will be disclosed after peer review.

We first present a comparison of the resistance of various DDFs against saturation, without any sliding window. This comparison helps us to choose the best subfilter.

Then, we design an experiment in which we compare the error rates of a QHT and a queuing filter, using the same QHT as a subfilter.

We remind the reader that for small sliding windows compared to the memory size, optimal or nearly optimal solutions can be implemented, as discussed in Section~\ref{sub:opt_solutions}. However, since we must evaluate the number of duplicates in the streams we use, we cannot benchmark our filter in real-life situations, as doing so would require way too much memory for keeping track of the duplicates.

>>>>

\subsection{Parameter Tuning}
\todo[FAUX, peut etre log ? However, practical tests show (see Section~\ref{sub:L_bench}) that setting $L = \sqrt w$ leads to optimal results.]

The parameters of a queueing filter are: the parameters of the subfilter, the number $L$ of subfilters and the number $c$ of insertions per subfilter.

@@

@@

\section{Experiments and Benchmarks}
This section provides details and additional information on the benchmarking experiments run to validate the above analysis. All code is accessible online and will be disclosed after peer review.

Our benchmarks cover two aspects: 
\begin{enumerate}
\item A measure of DDFs' saturation rate, in the original DDP setting (i.e. without a sliding window), which is used to choose a subfilter design;
\item A measure of the effect of queuing on error rates, in the sliding window DDP setting. Namely, we compate QHT and a queuing QHT.
\end{enumerate}
An important note is that when the sliding window is small compared to the filter's memory size, optimal or nearly optimal solutions can be implemented (see Section~\ref{sub:opt_solutions}). This is practical for smaller values because we can measure exactly a filter's response compared to the \enquote{ground truth}. However, this is no longer possible for very large parameters as it would require too much memory for keeping track of the duplicates.
